---
title: "Documentation"
output: html_document
date: "2024-09-12"
---


## Steps INVOLVE in creating a Package


1. next create a package project using the below code
```{r}
usethis::create_package(path = "C:/ETH/git/ETHdemo")
```
2. To create a new .R script inside the R/ directory of an R package project. use the code below
```{r}
usethis::use_r("StataExport")
```

3. create your function you want to use in StataExport.R file

4. Test functionality, allows you to test if your function does as expected
```{r}
devtools::load_all()
```
>devtools::load_all()
ℹ Loading StataExport

5. Document function
Go to “Code” and find “Insert Roxygen Skeleton”
    a. automate the creation and updating of documentation for R packages. It uses Roxygen2 comments to generate .Rd (manual) files and update the NAMESPACE file in your package, ensuring that everything is properly documented and registered for use.
```{r}
devtools::document()
```

> devtools::document()
ℹ Updating StataExport documentation
ℹ Loading StataExport
✖ StataExport.R:5: @param requires two parts: an argument name
  and a description.
✖ StataExport.R:6: @param requires two parts: an argument name
  and a description.
✖ StataExport.R:7: @param requires two parts: an argument name
  and a description.
✖ StataExport.R:10: @return requires a value.
✖ StataExport.R:13: @examples requires a value.
Writing NAMESPACE
Writing export_dynamic_crosstab.Rd
> 
Try ?times2 and notice a new folder called man

Try ?StataExport and notice a new folder called man
> ?StataExport
No documentation for ‘StataExport’ in specified packages and libraries:
you could try ‘??StataExport’
> 

## Git and GitHub
A few steps to go through

Setup user

```{r}
usethis::use_git_config(user.name = "rubbyaworka", user.email = "aworka123@gmail.com")
```

## Setup GitHub credentials

```{r}
credentials::set_github_pat()
```
> credentials::set_github_pat()
If prompted for GitHub credentials, enter your PAT in the password field
Using GITHUB_PAT from Rubby Aworka (credential helper: manager)

##Maybe you need to create a personal access token:
```{r}
usethis::create_github_token()
```

Use git: usethis::use_git()

Get package to GitHub
